\documentclass[12pt, a4paper]{article}


%=========================== PACKAGES =============================%
\usepackage[utf8]{inputenc}
\usepackage[hmargin=1.1cm,vmargin=1.1cm]{geometry}

%--- LANGUE--%
\usepackage[english]{babel}
\usepackage{hyperref}
%--- LANGUE--%

%--- FONT ----%
% \usepackage{helvet}
% \renewcommand{\familydefault}{\sfdefault}
%--- FONT ----%
%=========================== PACKAGES =============================%

\begin{document}

\pagestyle{empty} 

%======== PRENON ET NOM =========%
Gustavo CIOTTO PINTON
%======== PRENON ET NOM =========%

%======== ADRESSE ===============%
Rua Voluntário Amador Lourenço, 57

Valinhos, São Paulo, Brazil CEP 13271-393

+55 19 99898-5633

 \url{gustavociotto@gmail.com}

\url{https://github.com/gciotto/workspace/wiki/About-me}
%======== ADRESSE ===============%
\begin{flushright}
%======== VILLE ET DATE =========%
\vspace{-12pt}
Valinhos,  \today
%======== VILLE ET DATE =========%

%======== ENTREPRISE ===============%

%%%%%%% CHANGER 


%\vspace{12pt}

%A l'attention de \contactEntreprise
%======== ENTREPRISE ===============%
\end{flushright}

\textbf{Subject:} 6 to 12 - month internship in Brazil at Embraer

\vspace{12pt} 

To whom it may concern, 

\vspace{12pt}
%======== LETTRE ===============%
Currently in the ninth semester of the computer engineering course at
\textit{University of Campinas UNICAMP}, I am looking for an internship related
to the areas of embedded systems or information technology with  a duration of
between 6 and 12 months in Brazil, starting from January 2016. The
opportunity of working at a leading engineering company has always been one of my most relevant objectives considering my academic choices and, for this reason, an
internship at Embraer means a great step forward in my career. In this
way, since my admission at UNICAMP, I have been dedicating myself as much as possible to every
discipline taught during these last years. As a consequence of those
efforts, I have succeed in achieving a great academic performance, verified by
the high class rank I presently have. This qualification allowed me to apply
for, and subsequently to be selected for, a double degree program at
\textit{École Supérieure d'Electricité SUPELEC}, where I spent the last two
years studying electrical and computer engineering.  

\vspace{12pt}

Having fulfilled my first international academic experience, the requirement of
developing an activity in an engineering company became indispensable to my
professional growth. It is in this context that an internship at Embraer, a
leading enterprise in the aircraft market and one of the main actors in
engineering, represents a unique opportunity to improve all concepts acquired
so far through contact with key techniques used in large complex systems
nowadays.  One of the essential points consists in the fact that Embraer employs
many highly qualified employees who undoubtedly would help me a lot through
the exchange of experiences and acquisition of an effective and wide
network. In addition  to these features, Embraer constantly encourages
the process of innovation, allowing its workers to put forward their ideas and
suggestions, making the working environment much more pleasant and open to the
conception of new intelligent solutions. 


\vspace{12pt} 

With regard to my competences,  I believe the understanding of the concepts
involving programming is the most pertinent to this internship. During my time
in all the academic institutions where I studied and enterprises I worked for,
both in France and Brazil, I had close contact with many programming languages
and algorithms. At UNICAMP, I was assigned to perform twice the function of
laboratory assistant in two disciplines taught in the computer engineering
course: in the first discipline, I assisted the students during the lab
sessions, developed in C language, whose purpose was to explore concepts such as
arrays, sorting and search algorithms, recursion and pointers, and in
the second, the lab sessions explored some features of an ARM board, such as
interruptions, converters and serial transmission. Besides, during my first
professional experience, I was responsible to maintain the company's database
(MySQL Server) and web systems (written in PHP and
JavaScript). Another key aspect is the capacity of communicating with
other team members in many languages, since Embraer acts in many countries.
During my stay in France, I have achieved great results in the language certification exams that I took, such as TOELF ITP and
TCF, proving that I am able to work in multilingual environments.

	
\vspace{12pt}

Thank you for your time and effort taken when reviewing my application. I am
looking forward to your answer.

\vspace{12pt}

Yours sincerely,

\begin{flushright}
\textbf{Gustavo CIOTTO PINTON}
\end{flushright}
%======== LETTRE ===============%


\end{document}
