\documentclass[12pt, a4paper]{article}


%=========================== PACKAGES =============================%
\usepackage[utf8]{inputenc}
\usepackage[hmargin=0.5cm,vmargin=0.5cm]{geometry}

%--- LANGUE--%
\usepackage[english]{babel}
\usepackage{hyperref}
%--- LANGUE--%

%--- FONT ----%
% \usepackage{helvet}
% \renewcommand{\familydefault}{\sfdefault}
%--- FONT ----%
%=========================== PACKAGES =============================%

\begin{document}

\pagestyle{empty} 

%======== PRENON ET NOM =========%
Gustavo CIOTTO PINTON
%======== PRENON ET NOM =========%

%======== ADRESSE ===============%
Rua Voluntario Amador Lourenco, 57

Valinhos, Sao Paulo, Brazil CEP 13271-393

+55 19 99898-5633	

\url{gustavociotto@gmail.com}

\url{https://github.com/gciotto/workspace/wiki/About-me}
%======== ADRESSE ===============%
\begin{flushright}
%======== VILLE ET DATE =========%
Valinhos,  \today
%======== VILLE ET DATE =========%

%======== ENTREPRISE ===============%

%%%%%%% CHANGER 


%\vspace{12pt}

%A l'attention de \contactEntreprise
%======== ENTREPRISE ===============%
\end{flushright}

Dear Mr. , 

\vspace{12pt}
%======== LETTRE ===============%
Currently in the ninth semester of the computer engineering course at
\textit{Universidade Estadual de Campinas - UNICAMP}, I am looking for an
internship related to the areas of embedded systems and information technology
with duration between 6 and 12 months in France, starting from January 2016. The opportunity of
building an international career has always been one of my most relevant
objectives considering my academic choices and professional project. In this
way, since my admission in computer engineering at UNICAMP, I have been
dedicating myself as much as possible to every discipline taught during these
last years. As a consequence of those efforts, I have succeed in achieving a
great academic performance, verified by the high class rank I presently have: I am the second
best ranked student out of 97 enrolled in my promotion. This qualification
allowed me to apply for, and subsequently to be selected for, a double degree program
between UNICAMP and \textit{École Supérieure d'Electricité - SUPELEC}, one of
the main institutions of electrical and computer engineering in France. At this
occasion, I faced a highly-qualified competition, since only students
having the best grades in the whole school are allowed to join the selection
process. Thus, I spent the last two years studying in Paris, where I was able to 
improve my oral skills in both French and English and equally the concepts
taught in the engineering courses, such as signal processing, control,
electrotechnics and computing, for which I have always been among the best
students in the class.

\vspace{12pt}

Having fulfilled my first international academic experience, the requirement of
developing an activity in an engineering company became indispensable to my
professional growth. It is in this context that an internship at Airbus, a
leading enterprise in the aircraft market and one the main actors in
engineering, represents a unique opportunity to improve all concepts acquired
so far through contact with key techniques used in large complex systems
nowadays.  One of the essential points consists in the fact that Airbus employs
many highly qualified employees who undoubtedly would help me a lot through
the exchange of experiences and acquisition of an effective and wide
network. In addition  to these features, Airbus constantly encourages
the process of innovation, allowing its workers to put forward their ideas and
suggestions, making the working environment much more pleasant and open to the
conception of new intelligent solutions. Based on the experiences acquired
during my two years of exchange, I consider myself able to meet the challenges
posed by this internship, as I have always devoted my best to achieve the
proposed objectives and tasks as clearly and efficiently as possible, even with
many potential obstacles, such as a foreign language.


\vspace{12pt}

With regard to my competences,  I believe the understanding of the concepts
involving programming is the most pertinent to this internship. During my time
in all the academic institutions where I studied, both in France and Brazil, I
had close contact with many programming languages and algorithms, allowing me to perform
twice the function of laboratory assistant of two fundamental disciplines taught
in the computer engineering course at UNICAMP. For this reason, I can certainly
say I am prepared to perform the tasks assigned to me during the internship.
Another key aspect which is required in this internship is the capacity of
communicating with other team members in many languages, since Airbus is
composed of a multicultural staff. During my stay in France, I have achieved
results in the language certification exams that I took, proving
that I am able to work in multilingual environments. Thirdly, but not less
important, there is the commitment to results and quality. This competence is very important given
the competitive scope of the sector,  in which each existing alternative  in a
project must be exhaustively analyzed in order to find the best one.


	
\vspace{12pt}

Thank you for you time and effort taken when reviewing my application. I am
looking forward to your answer.

\vspace{12pt}

Yours sincerely,

\vspace{12pt}

\textbf{Gustavo CIOTTO PINTON}
%======== LETTRE ===============%


\end{document}
